Rasterizing prodution per each region

### 2021-08-12 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
cleaned up scripts and READMEs

---
title: "Location of Bivalve Farms"
author: "Gage Clawson (USCB, NCEAS, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Location of Bivalve Farms"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

### 2021-08-12 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
updated figs and stats with newly run farms
cleaned up scripts and READMEs

---
title: "Gapfilling the number of farms to add for bivalve countries based on tonnes of production"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

---
title: "Gapfilling the number of farms to add for bivalve countries based on tonnes of production"
output: html_document
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes the number of farms information collected in STEP2 and calculates a global tonnes of production per farm, and calculates the number of remaining farms needed to place in our placement model.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(dplyr)
library(tidyverse)
```

@@

write.csv(tonnes_per_farm, "output/bivalve_comp_tonnes_per_farm.csv", row.names = FALSE)

### 2021-08-12 marine/crustaceans/crustaceans_farms/STEP1_fao_crustacean_production.Rmd
cleaned up scripts and READMEs

---
title: "FAO crustaceam production"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "12/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

## write out crustacean taxa and production for Juliette
fao_crustaceans_taxa_prod <- fao %>%
  filter(species %in% crustaceans_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

write.csv(fao_crustaceans_taxa_prod, here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans_taxa_production.csv"), row.names=FALSE)

@@

 explore <- read_csv(here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100,2))

@@

>>>>

---
title: "FAO crustacean production"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "12/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Clean FAO crustacean data

@@

## write out crustacean taxa and production
fao_crustaceans_taxa_prod <- fao %>%
  filter(species %in% crustaceans_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year) %>%
  ungroup() %>%
  mutate(total = sum(fao_tonnes_production)) %>%
  mutate(perc = fao_tonnes_production/total)

## write out a file with the specific taxa included  
write.csv(fao_crustaceans_taxa_prod, here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans_taxa_production.csv"), row.names=FALSE)

@@

## explore the data     
 explore <- read_csv(here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100,2))

sum(explore$fao_tonnes_production) # 401719.1
unique(explore$country) # 6 countries

@@

```{r}
## look at crustacean taxa and production
fao_crustaceans_taxa_prod <- fao %>%
  filter(species %in% crustaceans_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_crustaceans_taxa_prod$value) # 401733.5 - adds 14 tonnes

unique(fao_crustaceans_taxa_prod$country) # 6 countries 
```

### 2021-08-12 marine/crustaceans/crustaceans_farms/STEP3_gapfill_crustaceans.Rmd
made the figures!
cleaned up scripts and READMEs

---
title: "Gapfilling the number of farms to add for shrimp countries based on tonnes of production"
output: html_document
---

@@

```{r}
avg_global_shrimp_tonnes_per_farm = 337.7357
avg_global_shrimp_tonnes_per_farm # 337.7357
```

>>>>

---
title: "Gapfilling the number of farms to add for crustacean countries based on tonnes of production"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes the number of farms information collected in STEP2 and calculates a global tonnes of production per farm, and calculates the number of remaining farms needed to place in our placement model.

@@

```{r}
avg_global_shrimp_tonnes_per_farm = 336.5783
avg_global_shrimp_tonnes_per_farm # 336.5783
```

### 2021-08-12 marine/last_step_rasterize/bivalve_rasterize_production.Rmd
cleaned up scripts and READMEs

# data <- read_csv("marine/output/all_marine_farms.csv") %>% 
#   st_as_sf(., 
#            coords = c("lon", "lat"),
#            crs = crs(food_raster), 
#            agr = "constant")

all_farms <- readRDS("data/all_modeled_marine_farms.rds")

# all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
#   map_df(., readRDS) %>% 
#   dplyr::rename(iso3c = iso3) %>% 
#   dplyr::mutate(source = "modeled") %>% 
#   rbind(data %>% mutate(source = "real"))

bivalve_farms <- all_farms %>%
  filter(type == "bivalve")

@@

# CHN:HKG
# CHN:MAC
# ESP:FRA
# HKG:CHN
# IRL:GBR
# NLD:DEU
# PRK:RUS
# SVN:HRV
# THA:MMR
# TWN:CHN
# USA:CAN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:FRA", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:FRA", "Spain", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "PRK:RUS", "PRK", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRK:RUS", "North Korea", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0))

@@

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

@@

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE) ## overwrite file if already there

@@

write_csv(bivalve_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/bivalve_farm_updated.csv")

>>>>

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
      st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

bivalve_farms <- all_farms %>%
  filter(species_group == "Unfed or algae fed bivalve molluscs")

@@

# CHN:HKG
# CHN:MAC
# CHN:PRK
# DEU:NLD
# HKG:CHN
# IRL:GBR
# MYS:BRN
# NLD:DEU
# SVN:HRV
# TWN:CHN
# USA:CAN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
    mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "DEU:NLD", "DEU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "DEU:NLD", "Germany", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
    mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0))

@@

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  # mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

@@

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/updated/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE) ## overwrite file if already there

@@

write_csv(bivalve_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/updated/bivalve_farm_updated.csv")

### 2021-08-12 marine/last_step_rasterize/crustaceans_rasterize_production.Rmd
cleaned up scripts and READMEs

# data <- read_csv("marine/output/all_marine_farms.csv") %>% 
#   st_as_sf(., 
#            coords = c("lon", "lat"),
#            crs = crs(food_raster), 
#            agr = "constant") %>%
#   mutate(source = "real")

all_farms <- readRDS("data/all_modeled_marine_farms.rds")

# all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
#   map_df(., readRDS) %>% 
#   rename(iso3c = iso3) %>% 
#  dplyr::mutate(source = "modeled") %>% 
#   #left_join(tonnage_per_farms)
#   rbind(data)

crust_farms <- all_farms %>%
  filter(type == "crustaceans")
```

@@

# some annoying mismatches due to raster resolution. Fix these
# CHN:HKG
# CHN:MAC
# MMR:THA

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% c("MMR:THA"), "MMR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% c("MMR:THA"), "Myanmar", NAME_0))

@@

crustacean_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
plot(log(crustacean_raster_check+1))
cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 401719.1

@@

write_csv(crustacean_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/crustaceans_farm_updated.csv")

>>>>

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
      st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

crust_farms <- all_farms %>%
  filter(species_group == "Non-shrimp crustaceans")
```

@@

# some annoying mismatches due to raster resolution. Fix these
# CHN:HKG
# CHN:PRK

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:PRK"), "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:PRK"), "China", NAME_0))

@@

crustacean_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
plot(log(crustacean_raster_check+1))
# s <- raster::select(crustacean_raster_check)
# plot(s)
cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 401719.1

@@

write_csv(crustacean_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/updated/crustaceans_farm_updated.csv")

### 2021-08-12 marine/last_step_rasterize/finfish_rasterize_production.Rmd
cleaned up scripts and READMEs

all_farms <- readRDS("data/all_modeled_marine_farms.rds")

finfish_farms <- all_farms %>%
  filter(type == "marine_fish_general")

@@

# CHN:HKG
# CHN:MAC
# CYP:XAD
# EGY:ISR
# ESP:PRT
# GRC:ALB
# GRC:TUR
# HKG:CHN
# MYS:IDN 
# PRT:ESP
# SGP:MYS
# TUR:GRC

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "EGY:ISR", "EGY", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "EGY:ISR", "Egypt", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GRC:ALB", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:ALB", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "GRC:TUR", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:TUR", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:IDN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:IDN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SGP:MYS", "SGP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "TUR:GRC", "TUR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TUR:GRC", "Turkey", NAME_0))

@@

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

farms_sf_prod <- st_as_sf(farms_prod)
mapview(farms_sf_prod)

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)

@@

finfish_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(finfish_raster + 1))

@@

write_csv(finfish_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/marine_fish_general_farm_updated.csv")

>>>>

# all_farms <- readRDS("data/all_modeled_marine_farms.rds")

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
      st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

finfish_farms <- all_farms %>%
  filter(species_group == "General marine fish")

@@

# CHN:HKG
# CHN:PRK
# CYP:XAD
# ESP:PRT
# GRC:ALB
# GRC:TUR
# HKG:CHN
# IDN:MYS
# MYS:BRN
# MYS:SGP
# SGP:MYS
# TWN:CHN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GRC:ALB", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:ALB", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "GRC:TUR", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:TUR", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:MYS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:MYS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SGP:MYS", "SGP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))

@@

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
 # mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

farms_sf_prod <- st_as_sf(farms_prod)
mapview(farms_sf_prod, cex = "tonnes_per_farm")

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/updated/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)

@@

finfish_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(finfish_raster + 1))
# s<-raster::select(finfish_raster)
# plot(s)

@@

write_csv(finfish_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/updated/marine_fish_general_farm_updated.csv")

### 2021-08-12 marine/last_step_rasterize/salmon_rasterize_production.Rmd
cleaned up scripts and READMEs

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

@@

all_farms <- readRDS("data/all_modeled_marine_farms.rds")

salmon_farms <- all_farms %>%
  filter(type == "salmon")

@@

mapview(filter(farms_sf, check == "RUS:RUS"))
mapview(farms_sf)
# some annoying mismatches due to raster resolution. Fix these

@@

salmon_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(salmon_raster + 1))

@@

write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/salmon_farm_updated.csv")

>>>>

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)

@@

# all_farms <- readRDS("data/all_modeled_marine_farms.rds")

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
      st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

salmon_farms <- all_farms %>%
  filter(species_group == "Salmonidae fish")

@@

mapview(filter(farms_sf, check == "RUS:RUS"))
mapview(farms_sf, cex = "tonnes_per_farm")
# some annoying mismatches due to raster resolution. Fix these

@@

salmon_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(salmon_raster + 1))
# s <- raster::select(salmon_raster)
# plot(s)

@@

write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/updated/salmon_farm_updated.csv")
